% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=mygreylink     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{{\LARGE Nathaniel Nguyen}} & \href{mailto:nnguyen939@gmail.com}{nnguyen939@gmail.com}\\
	{\footnotesize \texttt{{120 202nd ST SE Bothell WA 98012}}} & 
	{Cell:  206.393.8363}
	\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{{Skills}}
	\begin{description}
		\item[Technologies:] { \footnotesize Ada, C/C++, Java, Ruby, Python, MySQL, Regex, Unix Shell, {\LaTeX}, GIT, Mecurial, JSON, XML, Maven, Gnu Make, Cobertura, FindBugs, Checkstyle, AWS S3, AWS SQS}
		\item[Computer and OS:] { \footnotesize Linux, Windows, Mac OS X}
		\item[Software:]{\footnotesize
			{MS Visual Studio},
			{Eclipse IDE},
			{Vi/Vim}, {IntelliJ IDEA}} 
		\item[Others:] {\footnotesize OO programming, functional programming,  test driven development, Scrum,  Kanban, deployment and release processes, SaaS, Continuous Deployment/Delivery}
	\end{description} % End Skills list
	
%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
	\begin{description}
		 {\footnotesize 
			\item \ressubheading{{Amazon Web Services -- Builder Tool's Apollo team }}{Seattle, WA}{Software Development Engineer}{Oct. 2014 -- Current}
				\begin{itemize}
					\resitem{Worked as part of the oncall rotation to handle and resolve customer impacting issues in Apollo}
					\resitem{Worked with multiple internal teams to design and re-architect Apollo to handle Amazon rapidly changing network architecture  }					
					\resitem{Improved the visibility of Apollo's "EC2" services which allowed oncalls to identified regional issues }
					\resitem{Acted as a TPM to migrate thousands of internal customers using a deprecated software owned by Apollo }
				\end{itemize}
			\item \ressubheading{{Amazon Web Services -- Builder Tool's Apollo team }}{Seattle, WA}{Software Development Engineer in Test}{Jan. 2014 -- Oct. 2014}
				\begin{itemize}
					\resitem{Implemented a test framework to allow developers of AWS CodeDeploy to write tests with}
					\resitem{Implemented a load test tool to allow developers of AWS CodeDeploy to load test with}
					\resitem{Designed and implemented a test plan for Apollo's client side codebase and reduced several hours of manual testing to twenty minutes of automated testing}
					\resitem{Promoted an internal testing pattern for Apollo's twenty-plus services}
				\end{itemize}
			\item \ressubheading{{Amazon E-commerce and Platform -- Web Application and Platform's QA Team}}{Seattle, WA}{Software Development Engineer in Test}{Oct. 2013 -- Jan. 2014}
				\begin{itemize}
					\resitem{Designed and implemented a test plan to allow Amazon's email team to move to a Continuous Deployment pipeline }
					\resitem{Identified and designed TOP team released process into restricted regions}
				\end{itemize}
			\item \ressubheading{{LizardTech }}{Seattle, WA}{Intern}{Sept. 2012 -- Jun. 2013}
				\begin{itemize}
					\resitem{Developed a web application to save selected regions of raster images in multiple format and size}
					\resitem{Developed in Java}
					\resitem{Used Maven and Mecurial to manage the project}
				\end{itemize}
			}



	\end{description} % End Skills list
	
%%%%%%%%%%%%%%%%%%%%%%	
\resheading{Education}
	\begin{itemize}
		\item
			\ressubheading{{Western Washington University}}{Bellingham, WA}{{Bachelor of Science in Computer Science}}{Sept. 2010 -- Jun. 2013}
			
		\item
			\ressubheading{{Edmonds Community College}}{Lynnwood, WA}{{Associate of Science}}{Sept. 2008 -- Jun. 2010}

	\end{itemize} % End Education list






\end{document}









